---
title: "Portfolios"
author: "Eliesha Lai"
date: "2020/8/16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r library,warning=FALSE, message=FALSE}
  
library(mosaic)
library(quantmod)
library(foreach) 

```

## First Portfolio

We chose Amazon, Visa, First Trust Technology AlphaDEX® Fund, and Best Buy as a combination of ETF.Next step, we extracted data from 2015, which was five years ago.
With agjusting all stocks, we can then calculate the returns of each stocks, and put them in a matrix.

```{r first portfolio ,message=FALSE,results = "hide",warning=FALSE}
# Technology Equity ETF:  FXL	First Trust Technology AlphaDEX Fund
mystocks = c("AMZN", "V", "FXL","BBY")
myprices = getSymbols(mystocks, from = "2015-01-01")

#adjusting all stocks
for(ticker in mystocks) {
  expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
  eval(parse(text=expr))
}
```

```{r }
head(AMZNa)

# Combine all the returns in a matrix
all_returns = cbind(ClCl(AMZNa),ClCl(Va),ClCl(FXLa),ClCl(BBYa))
head(all_returns)
```

```{r}
all_returns = as.matrix(na.omit(all_returns))

# Compute the returns from the closing prices
pairs(all_returns)


```


```{r first, results = "hide",message=FALSE }

# simulate many different possible futures
initial_wealth = 100000
sim1 = foreach(i=1:50000, .combine='rbind') %do% {
  total_wealth = initial_wealth
  weights = c(0.25, 0.25, 0.25, 0.25)
  holdings = weights * total_wealth
  n_days = 20 #4 weeks
  wealthtracker = rep(0, n_days)
  for(today in 1:n_days) {
    return.today = resample(all_returns, 1, orig.ids=FALSE)
    holdings = holdings + holdings*return.today
    total_wealth = sum(holdings)
    wealthtracker[today] = total_wealth
  }
  wealthtracker
}
head(sim1)
```

```{r}
hist(sim1[,n_days], 80) #80 bins
# I have some great outliner...
range(sim1[,n_days])


```

```{r first profit/loss}
# Profit/loss
mean(sim1[,n_days])
mean(sim1[,n_days] - initial_wealth)
hist(sim1[,n_days]- initial_wealth, breaks=100)

# 5% value at risk:
quantile(sim1[,n_days]- initial_wealth, prob=0.05)


```
There is 5% of chance my simulated futures will have a loss of worse than $8292.279

95% of chance the simulated futures are better than losing $8292.279

------------------------------------

## Second Portfolio

Agricultural Commodities ETFs -FUD : E-TRACS UBS Bloomberg CMCI Food ETN

Money Market IBMI: iShares iBonds Sep 2020 AMT-Free Muni Bond ETF

Global Real Estate ETFs -GQRE: FlexShares Global Quality Real Estate Index Fund

Global Equities ETFs -INKM: SPDR SSgA Income Allocation ETF

```{r second portfolio ,warning=FALSE,results = "hide",message=FALSE }


mystocks = c("FUD", "IBMI","GQRE","INKM")
myprices = getSymbols(mystocks, from = "2015-01-01")

#adjusting all stocks
for(ticker in mystocks) {
  expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
  eval(parse(text=expr))
}
```

```{r}
head(FUDa)

# Combine all the returns in a matrix
all_returns = cbind( ClCl(FUDa),
                     ClCl(IBMIa),
                     ClCl(GQREa),
                     ClCl(INKMa)
                    )
head(all_returns)

```

```{r}
all_returns = as.matrix(na.omit(all_returns))
# Compute the returns from the closing prices
pairs(all_returns)


```

```{r second ,results = "hide", message=FALSE}
# simulate many different possible futures
initial_wealth = 100000
sim1 = foreach(i=1:50000, .combine='rbind') %do% {
  total_wealth = initial_wealth
  weights = c(0.25, 0.25, 0.25, 0.25)
  holdings = weights * total_wealth
  n_days = 20 #4 weeks
  wealthtracker = rep(0, n_days)
  for(today in 1:n_days) {
    return.today = resample(all_returns, 1, orig.ids=FALSE)
    holdings = holdings + holdings*return.today
    total_wealth = sum(holdings)
    wealthtracker[today] = total_wealth
  }
  wealthtracker
}

head(sim1)
```

```{r}
hist(sim1[,n_days], 25) #25 bins

```

```{r second profit/loss}
# Profit/loss
mean(sim1[,n_days])
mean(sim1[,n_days] - initial_wealth)
hist(sim1[,n_days]- initial_wealth, breaks=30)

# 5% value at risk:
quantile(sim1[,n_days]- initial_wealth, prob=0.05)

```
There is 5% of chance my simulated futures will have a loss of worse than $4352.73

95% of chance the simulated futures are better than losing $4352.73

------------------------------------

## Third Portfolio

RJZ: RICI-Metals ETN

SVXY:	ProShares Short VIX Short-Term Futures

SPVM:	Invesco S&P 500 Value with Momentum ETF

IGM:	iShares Expanded Tech Sector ETF

VBK:	Vanguard Small Cap Growth ETF

```{r third portfolio ,results = "hide",message=FALSE, warning=FALSE }

mystocks = c("RJZ", "SVXY","SPVM","IGM","VBK")
myprices = getSymbols(mystocks, from = "2015-01-01")

#adjusting all stocks
for(ticker in mystocks) {
  expr = paste0(ticker, "a = adjustOHLC(", ticker, ")")
  eval(parse(text=expr))
}
```

```{r}
head(FUDa)

# Combine all the returns in a matrix
all_returns = cbind( ClCl(RJZa),
                     ClCl(SVXYa),
                     ClCl(SPVMa),
                     ClCl(IGMa),
                     ClCl(VBKa)
                     )
head(all_returns)
```

```{r}
all_returns = as.matrix(na.omit(all_returns))

# Compute the returns from the closing prices
pairs(all_returns)

```





```{r third ,results = "hide",message=FALSE}

# simulate many different possible futures
initial_wealth = 100000
sim1 = foreach(i=1:50000, .combine='rbind') %do% {
  total_wealth = initial_wealth
  weights = c(0.2,0.2,0.2,0.2,0.2)
  holdings = weights * total_wealth
  n_days = 20 #4 weeks
  wealthtracker = rep(0, n_days)
  for(today in 1:n_days) {
    return.today = resample(all_returns, 1, orig.ids=FALSE)
    holdings = holdings + holdings*return.today
    total_wealth = sum(holdings)
    wealthtracker[today] = total_wealth
  }
  wealthtracker
}

head(sim1)
```

```{r}
hist(sim1[,n_days], 25) #25 bins

```


```{r third Profit/loss}
# Profit/loss
mean(sim1[,n_days])
mean(sim1[,n_days] - initial_wealth)
hist(sim1[,n_days]- initial_wealth, breaks=30)

# 5% value at risk:
quantile(sim1[,n_days]- initial_wealth, prob=0.05)

```
There is 5% of chance my simulated futures will have a loss of worse than $-11462.21

95% of chance the simulated futures are better than losing $-11462.21





















