---
title: "Q1"
author: "Xuxian Chen"
date: "8/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mosaic)
library(tidyverse)
library(ggplot2)
```

# Q1 CSV

```{r gb}
gb <- read.csv("../STA380/data/greenbuildings.csv")
head(gb)
gb$green_rating = as.factor(gb$green_rating)
```

## Graphic Presentation and Analysis

### Does green housing have a higher rental price
```{r pressure, echo=FALSE}
ggplot(data = gb) + 
  geom_point(mapping = aes(x = cluster_rent, y = Rent, color = green_rating)) +
  labs(title = "Rental Price of Green Building and NonGreen Building",
       subtitle="Across All Clusters")
```
There is large variation and outliners in the dataset. The eco-friendly building appears to have higher rental rate comparatively, looking at the same cluster_rent level.

### What percentage of green buildings having a higher rental price than local market rental price? What about percentage of nongreen buildings?

```{r}
d1 = gb %>%
  group_by(green_rating ) %>%
  summarize(good_performance = sum(Rent > cluster_rent)/n())

ggplot(data = d1) + 
  geom_bar(mapping = aes(x = green_rating, y = good_performance ), stat='identity') +
  labs(title = "Percentage of Buildings with Higher Rental Rate than Local Market Rental Rate")+ 
  coord_flip()
```
**Proportionally, more green buildings have higher than market rental rate**

### Reproduce the analysis of the excel guru to validate
```{r}
gb_filtered = filter(gb, leasing_rate>.1)

gb_filtered %>%
  group_by(green_rating) %>%
  summarize(Rent.med = median(Rent))
```
So far the results support the EXCEL guru's analysis, that green buildings have a higher rental price comparatively. 
Green Buildings have a 27.6 vs Nongreen Buildings' 25, but we want to know if green or nongreen causes the difference in price. In another words, how other factors play in determining rental rate?

### Could it be: NonGreen building are mostly older buildings?
```{r}
ggplot(data = gb) + 
  geom_point(mapping = aes(x = age, y = Rent, color = green_rating))+
  labs(title = "Building Rent with different BUilding Age")
```
The green building did not show a strong pattern in higher rent, given the same building age

### Could it be: Most Green buildings are renovated?
```{r}
gb %>%
  group_by(green_rating) %>%
  summarize(renovated.count = count(renovated > 0))

gb_filtered = filter(gb, renovated>0)

ggplot(data = gb_filtered) + 
  geom_point(mapping = aes(x = cluster_rent, y = Rent, color = green_rating),stat='identity') +
  labs(title = "Renovated Building in Local Market")
```
If both are renovated, green buildings generally have a higher rental price than the nongreen buildings in the same local market.


### If we estimated the return of Green and NonGreen building of similar conditions
```{r}
hist(gb$stories)
hist(gb$age)

gb_filtered = filter(gb, 20 > stories, stories > 10, age < 25, age > 10)

ggplot(data = gb_filtered) + 
  geom_point(mapping = aes(x = cluster_rent, y = Rent, color = green_rating)) +
  labs(title = "Rent per Square of Green Building and NonGreen Building in Similar Condition")
gb_filtered %>%
  group_by(green_rating) %>%
  summarize(Rent.med = median(Rent))
```
There is a small green building premium but it is not as high as the EXCEL Guru estimated.

## Modeling
So far we have seen how green building appear to have a higher rantal rate, but we still cannot prove green building is having a higher rental rate. It could be an indirect results of others factors.

