---
title: "sta380 part2 exercises"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Visual story telling part 1: green buildings

```{r cars}
green = read.csv('greenbuildings.csv', header=T)

```

```{r}
hist(not_green$Rent, 25)
mean(not_green$Rent)
```

```{r}
hist(green_only$Rent, 25)
mean(green_only$Rent)
```

```{r}
xbar = mean(green_only$Rent)
sig_hat = sd(green_only$Rent)
se_hat = sig_hat/sqrt(nrow(green_only))
xbar + c(-1.96,1.96)*se_hat

#normal confidence interval for sample mean
```
```{r}
model1 = lm(Rent ~ 1, data=green_only)
confint(model1, level=0.95)
```

```{r}
#bootstrapping
library(mosaic)
green_only_boot = resample(green_only)
mean(green_only_boot$Rent)

```

```{r}
model2 = lm(Rent ~ 1, data=not_green)
confint(model2, level=0.95)
```

```{r}
green_all_boot = resample(not_green)
mean(not_green$Rent)
```

Some exploratory data to get a feel for the dataset. We can understand here the relationship between rent for green buildings and rent for not buildings. It is confirmed here that the difference between the rent prices exists for green biuldings and not green buidlings. At a 97.5% confideence interval, we are able to see that the interval for rent prices for not green buildings does not overlap with the green interval rents, showing that there is a higher cost (or more revenue) from having a green building. However, is it because it is green, or some other variable in the background that is correlated with green buildings, that drives up rent prices?

To take a deeper look at this, I decided to do a stepwise regression model for: all buildings, green only, and not green buildings to see what variables impacted rent the most, and if there were any changes or patterns among these.

For all buildings, we had an AIC=-10971.86
rent_all ~ Rent + total_dd_07 + cluster_rent + Electricity_Costs +  age

It seems for all buildings, what impacts rent the most would be:
* the age of a building, which makes sense, the older the building, the more depreciated, and the less valued by customers and the market
* cluster rent (a measure of average rent per square-foot per calendar year in the building's local market) which makes sense, because if the market is in new york, it will be more expensive than texas
* total.dd.07 the total number of degree days (either heating or cooling) in the building's region in 2007, this one seemed not as obvious to me but, seeing electricity costs is also on here, the correlation between degrees and electricity costs has a correlation of 0.67, showing there is some correlation. the higher it is outside, the colder it will be inside and vice versa
* electricity costs makese sense since it is a variable costs and is paid monthly just like rent, can determine the overall amount charged

For green buildings, we had an AIC=-1319.5

green_rent ~ Rent + total_dd_07 + Electricity_Costs + cluster_rent

As explained above, this contains everything but age

To measure if this is different than buildings that are not green
we had an AIC=-11140.9
not_green_rent ~ Rent + total_dd_07 + cluster_rent + Electricity_Costs + age

The only thing that varies from all buildings, not green buildings and the green buildings is that green buildings are not as impacted by age.

As we take the mean and median age for buildings, green_only has a mean age of 23.84526 and a median of 22 while not green buildings are much older with  a mean of 49.46733 and a median of 37.

While measuring the correlation between rent price and age it shows only a 0.10, the prices could be determined another way (cluster rent and rent have a correlation of 0.7593399). Having such a big difference in age of buildings could suggest that since green buildings are often newer, they have nicer places and people usually pay more for newer buildings.

However, another reason could be electricity costs. 
Green buildings have a higher correlation with the total.dd.07 and elecrticity costs (-0.7178119) than all buildings (-0.657102) and not green buildings (0.6522979). This could suggest that green buildings are impacted more by the heat and therefore use electricity more or less accordingly. Green buildings also have a higher mean average for electricity costs (0.03158175) than non green buildings (0.03089946) showing they do on average spend more on electricity. More electricty usage, more electricity costs and bills, higher rent, and higher revenue. This makes sense because while green buildings try to lower costs such as water, lighting, disposal etc, this is coming from somewhere else (solar panels, different sources of heating) that could affect electricity in different ways or even cause their customers to seek to use more electricity.

I believe there is possibility of confounding variables for the relatoinship between rent and green status. Affirmed by our stepmodels, green status wasn't even chosen as a significant variable in any of the samples, showing that it might not be the reason for rent prices. 

Furthermore, there's a lot that goes into rent prices, such as the area you live in, how old the building is, etc. When looking at green buildings, you are looking at newer buildings, and the fact that the building is new could affect the amount you charge for rent. When looking at the energy source changes for green buildings, there is always an effect of redirection of that energy, and that confounding variable could come from the electricity bills.

I believe that the developer should look further into resources to determine what exactly causes rent prices to be higher, and I believe it is not due to it being green, but the effects and attributes that being green has. You do not want to solely base your profit off being green, because following this model, each year you would make less due to the building getting older, or maybe higher electricity costs for the company to maintain being green. You need to see specifically what is causing a higher rent price, and not rely on just being green because background variables are at work here.

```{r}
cor(green$total_dd_07, green$Electricity_Costs)
```
```{r}
mean(green_only$age)
median(green_only$age)
```
```{r}
mean(not_green$age)
median(not_green$age)
```
```{r}
cor(green$Rent, green$age)
```
```{r}
cor(green$Rent, green$cluster_rent)
```


```{r}
print(cor(green_only$Rent, green_only$Electricity_Costs))
plot(green_only$Rent, green_only$Electricity_Costs)
```
```{r}
cor(green$Rent, green$Electricity_Costs)
plot(green$Rent, green$Electricity_Costs)
```

```{r}
print(cor(green_only$total_dd_07, green_only$Electricity_Costs))
plot(green_only$total_dd_07, green_only$Electricity_Costs)
```

```{r}
print(cor(green$total_dd_07, green$Electricity_Costs))
plot(green$total_dd_07, green$Electricity_Costs)
```
```{r}
print(cor(not_green$total_dd_07, not_green$Electricity_Costs))

```


```{r}
mean(green_only$Electricity_Costs)
```

```{r}
mean(not_green$Electricity_Costs)
```



```{r}
#Let us use the log response
rent_all <- log(green$Rent)

#subset of dataset for simplicity, dont do this try to include all in dataset
all_sub <- green[,-c(0,1,2,3)] # lose lmedval and the room totals
n = dim(all_sub)[1] #Sample size
tr = sample(1:n, #Sample indices do be used in training
            size = 3000, #Sample will have 5000 observation
            replace = FALSE) #Without replacement


#Create a full matrix of interactions (only necessary for linear model)
#Do the normalization only for main variables.
xxall_rent_sub <- model.matrix(~., data=data.frame(scale(all_sub)))[,-1] # the . syntax multiplies data by each long and lat, and then by both
allData = data.frame(rent_all,all_sub)

#Two models initially, sets the scope/boundaries for search
null = lm(rent_all~1, data=allData[tr,]) #only has an intercept
full = glm(rent_all~., data=allData[tr,]) #Has all the selected variables

#Let us select models by stepwise


regBack = step(full, #Starting with the full model
               direction="backward", #And deleting variables
               k=log(length(tr))) #This is BIC


regForward = step(null, #The most simple model
                  scope=formula(full), #The most complicated model
                  direction="both", #Add or delete variables
                  k=log(length(tr))) #This is BIC

#the total number of degree days (either heating or cooling) in the building's region in 2007.


'''
Step:  AIC=-10971.86
rent_all ~ Rent + total_dd_07 + cluster_rent + Electricity_Costs + 
    age

using the 2969/3000 rows from a combined fit                    Df Sum of Sq     RSS      AIC
<none>                            76.178 -10971.9
+ class_a            1     0.610  74.189 -10897.7
+ amenities          1     0.450  74.349 -10891.3
+ renovated          1     0.359  74.440 -10887.7
+ empl_gr            1     0.214  74.585 -10881.9
+ leasing_rate       1     0.190  74.609 -10880.9
+ Gas_Costs          1     0.156  74.644 -10879.5
+ class_b            1     0.134  74.665 -10878.7
+ stories            1     0.095  74.704 -10877.1
+ cd_total_07        1     0.088  74.711 -10876.9
+ hd_total07         1     0.088  74.711 -10876.9
+ net                1     0.046  74.754 -10875.2
+ green_rating       1     0.040  74.760 -10874.9
+ Energystar         1     0.036  74.763 -10874.8
+ Precipitation      1     0.002  74.798 -10873.4
+ LEED               1     0.001  74.798 -10873.4
- Electricity_Costs  1     2.974  79.152 -10865.0
- age                1     3.158  79.336 -10858.0
- cluster_rent       1     8.101  84.278 -10676.7
- total_dd_07        1     8.928  85.105 -10647.4
- Rent               1   137.313 213.490  -7888.3
'''
```


```{r}
# Extract the buildings with green ratings
green_only = subset(green, green_rating==1)#Let us use the log response
green_rent <- log(green_only$Rent)

#subset of dataset for simplicity, dont do this try to include all in dataset
green_rent_sub <- green_only[,-c(0,1,2,3)] # lose lmedval and the room totals
n = dim(green_rent_sub)[1] #Sample size
tr = sample(1:n, #Sample indices do be used in training
            size = 300, #Sample will have 5000 observation
            replace = FALSE) #Without replacement


#Create a full matrix of interactions (only necessary for linear model)
#Do the normalization only for main variables.
xxgreen_rent_sub <- model.matrix(~., data=data.frame(scale(green_rent_sub)))[,-1] # the . syntax multiplies data by each long and lat, and then by both
greenData = data.frame(green_rent,green_rent_sub)

#Two models initially, sets the scope/boundaries for search
null = lm(green_rent~1, data=greenData[tr,]) #only has an intercept
full = glm(green_rent~., data=greenData[tr,]) #Has all the selected variables

#Let us select models by stepwise

regBack = step(full, #Starting with the full model
               direction="backward", #And deleting variables
               k=log(length(tr))) #This is BIC
regForward = step(null, #The most simple model
                  scope=formula(full), #The most complicated model
                  direction="both", #Add or delete variables
                  k=log(length(tr))) #This is BIC

#Step:  AIC=-1319.5 green_rent ~ Rent + total_dd_07 + Electricity_Costs + cluster_rent

```

```{r}
not_green = subset(green, green_rating==0)
dim(not_green)

#Let us use the log response
not_green_rent <- log(not_green$Rent)

#subset of dataset for simplicity, dont do this try to include all in dataset
not_green_sub <- not_green[,-c(0,1,2,3)] # lose lmedval and the room totals
n = dim(not_green_sub)[1] #Sample size
tr = sample(1:n, #Sample indices do be used in training
            size = 3000, #Sample will have 5000 observation
            replace = FALSE) #Without replacement


#Create a full matrix of interactions (only necessary for linear model)
#Do the normalization only for main variables.
xxnot_green_sub <- model.matrix(~., data=data.frame(scale(not_green_sub)))[,-1] # the . syntax multiplies data by each long and lat, and then by both
notgreenData = data.frame(not_green_rent,not_green_sub)

#Two models initially, sets the scope/boundaries for search
null = lm(not_green_rent~1, data=notgreenData[tr,]) #only has an intercept
full = glm(not_green_rent~., data=notgreenData[tr,]) #Has all the selected variables

#Let us select models by stepwise

regBack = step(full, #Starting with the full model
               direction="backward", #And deleting variables
               k=log(length(tr))) #This is BIC
regForward = step(null, #The most simple model
                  scope=formula(full), #The most complicated model
                  direction="both", #Add or delete variables
                  k=log(length(tr))) #This is BIC
'''
Step:  AIC=-11140.9
not_green_rent ~ Rent + total_dd_07 + cluster_rent + Electricity_Costs + 
    age

using the 2971/3000 rows from a combined fit                    Df Sum of Sq     RSS      AIC
<none>                            89.857 -10484.4
+ Electricity_Costs  1     2.757  86.365 -10463.6
+ amenities          1     1.529  87.592 -10421.6
+ cd_total_07        1     1.365  87.757 -10416.1
+ hd_total07         1     1.365  87.757 -10416.1
+ class_a            1     0.814  88.308 -10397.5
+ leasing_rate       1     0.724  88.398 -10394.4
+ renovated          1     0.338  88.784 -10381.5
+ stories            1     0.279  88.843 -10379.5
+ Gas_Costs          1     0.272  88.850 -10379.3
+ empl_gr            1     0.167  88.954 -10375.8
- age                1     3.564  93.420 -10375.7
+ Precipitation      1     0.008  89.113 -10370.5
+ net                1     0.003  89.119 -10370.3
+ class_b            1     0.000  89.122 -10370.2
- total_dd_07        1     5.214  95.071 -10323.2
- cluster_rent       1    12.932 102.789 -10089.1
- Rent               1   121.564 211.421  -7925.5
'''

```


## Visual story telling part 2: flights at ABIA



